### 2014-10-22 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Added Figures

@@

>>>>

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_11_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_11_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_12_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_12_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_13_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_13_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_14_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_14_Second_Suppression}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_1_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_1_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_2_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_2_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, First Suppression}
	\label{fig:Test_3_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, Second Suppression}
	\label{fig:Test_3_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, First Suppression}
	\label{fig:Test_4_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, Second Suppression}
	\label{fig:Test_4_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_5_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_5_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_6_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_6_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
	\label{fig:Test_7_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
	\label{fig:Test_7_Second_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
	\label{fig:Test_8_First_Suppression}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
	\label{fig:Test_8_Second_Suppression}
\end{figure}
